Considering scale in multilayer animal social networks

### 2020-06-26 paper/manuscript.Rmd
todos

Multilayer networks represent a novel framework for explicitly testing the
influence of habitat selection on sociality across scales. Animal social systems
can be parsed by spatial contexts, for example as defined by habitat type as in
Figure \@ref(fig:lcres). Since habitat data are available across a range of
spatial scales, we evaluated the influence of increasing spatial resolution on
multilayer network metrics. As spatial resolution increased, edge overlap
remained stable in open and forest layers but decreased in foraging layers
(Figure \@ref(fig:lcres) D). Graph strength did not change in forest layers
with increasing spatial resolution (Figure \@ref(fig:lcres) E). Foraging and
open layer had greater individual variation in graph strength, and foraging
layers showed an increase in graph strength with increasing spatial resolution
(Figure \@ref(fig:lcres) E). Foraging habitat is rare (12.8% of the landscape)
on Fogo Island and the proportion of relocations in foraging habitat decreased
as spatial resolution increased (14.5% at 30 m - <2% at 1000 m). Despite this,
the foraging layer had similar edge overlap as the open layer at 30 m resolution 
indicating its importance in caribou sociality. As such, multilayer network
measures related to habitat are explicitly dependent on spatial scale.  If the
spatial resolution of the habitat data are insufficient to capture rare
habitats, for example, context-specific relationships between individuals may
not be captured.
<!-- habitat+social -->

<!-- mov -->
Social processes, movement decisions, and space use are inextricably linked and
multilayer networks represent a potential analytical framework for linking these
processes [@Mourier_2019]. Collective movement can reduce per capita predation
risk via detection-dilution trade-offs and improve information transfer about
the quality or location of resources [@Jolles_2019]. Multilayer networks could
be constructed from layers defined by movement parameters, given the existing
framework using behavioural layers [e.g. @Smith_Aguilar_2019]. For example,
edges could represent measures of collective movement based on dynamic
interaction metrics [@Long_2014]. We generated multilayer networks based on
habitat-specific layers of social association. Integrating habitat-specific
movement layers could further illuminate the role of movement as a driver of the
social and spatial environments an individual experiences [@Webber_2018]. For
example, social processes may be an emergent property of the landscape because
animals aggregate at resources, such as waterholes [@Chamaill_Jammes_2008].
Movement to, from, or within habitat patches or territories can also contribute
to the formation of the social environment [@Spiegel_2016]. For example, in
sleepy lizards (*Tiliqua rugosa*) males interacted primarily at home range
edges, presumably driving territorial behaviour [@Spiegel_2018]. Incorporating
movement ecology within a multilayer network framework is a logical next step
for a burgeoning field. Importantly, the technological advancements in
biologging and wildlife tracking technology [@Border_2020] have enabled this
unique opportunity to integrate movement and habitat in multilayer networks to
answer complex questions about animal socioecology.
<!-- mov -->

@@

<!-- nobs -->
It is crucial to include sufficient data within sampling periods or time windows
to construct robust networks [@Farine_2017; Proskurnikov_2017]. To test the
influence of data quantity on multilayer networks, we generate multilayer networks
using a subset of observations. Variance decreased across all
network metrics in all three habitat layers with increasing number of
observations. Individual graph strength showed high variability at low number of
observations, while edge overlap and multidegree increased sharply. After
approximately 200 observations, the rate of change for all metrics decreased and
and graph strength remained relatively static, while edge overlap and
multidegree continued to increase slowly. As more observations were added, rarer
relationships were recorded revealing the value of this form of sensitivity
analysis. Finally, due to the autocorrelated nature of biologging data it is
essential to ensure social association data area non-randomly distributed
[@Farine_2017b].
<!-- nobs -->

>>>>

Multilayer networks represent a novel framework for explicitly testing the
influence of habitat selection on sociality across scales <!-- TODO: add fig 6-->. Animal social systems
can be parsed by spatial contexts, for example as defined by habitat type as in
Figure \@ref(fig:lcres). Since habitat data are available across a range of
spatial scales, we evaluated the influence of increasing spatial resolution on
multilayer network metrics. As spatial resolution increased, edge overlap
remained stable in open and forest layers but decreased in foraging layers
(Figure \@ref(fig:lcres) D). Graph strength did not change in forest layers
with increasing spatial resolution (Figure \@ref(fig:lcres) E). Foraging and
open layer had greater individual variation in graph strength, and foraging
layers showed an increase in graph strength with increasing spatial resolution
(Figure \@ref(fig:lcres) E). Foraging habitat is rare (12.8% of the landscape)
on Fogo Island and the proportion of relocations in foraging habitat decreased
as spatial resolution increased (14.5% at 30 m - <2% at 1000 m). Despite this,
the foraging layer had similar edge overlap as the open layer at 30 m resolution 
indicating its importance in caribou sociality. As such, multilayer network
measures related to habitat are explicitly dependent on spatial scale.  If the
spatial resolution of the habitat data are insufficient to capture rare
habitats, for example, context-specific relationships between individuals may
not be captured.
<!-- habitat+social -->

<!-- mov -->
Social processes, movement decisions, and space use are inextricably linked and
multilayer networks represent a potential analytical framework for linking these
processes [@Mourier_2019]. Collective movement can reduce per capita predation
risk via detection-dilution trade-offs and improve information transfer about
the quality or location of resources [@Jolles_2019]. Multilayer networks could
be constructed from layers defined by movement parameters, given the existing
framework using behavioural layers [e.g. @Smith_Aguilar_2019]. For example,
edges could represent measures of collective movement based on dynamic
interaction metrics [@Long_2014]. We generated multilayer networks based on
habitat-specific layers of social association. Integrating habitat-specific
movement layers could further illuminate the role of movement as a driver of the
social and spatial environments an individual experiences [@Webber_2018]. For
example, social processes may be an emergent property of the landscape because
animals aggregate at resources, such as waterholes [@Chamaill_Jammes_2008].
Movement to, from, or within habitat patches or territories can also contribute
to the formation of the social environment [@Spiegel_2016]. For example, in
sleepy lizards (*Tiliqua rugosa*) males interacted primarily at home range
edges, presumably driving territorial behaviour [@Spiegel_2018]. Incorporating
movement ecology within a multilayer network framework is a logical next step
for a burgeoning field. Importantly, the technological advancements in
biologging and wildlife tracking technology <!-- TODO: fix-->[@Border_2020] have enabled this
unique opportunity to integrate movement and habitat in multilayer networks to
answer complex questions about animal socioecology.
<!-- mov -->

@@

<!-- nobs -->
It is crucial to include sufficient data within sampling periods or time windows
to construct robust networks <!--TODO check--> [@Farine_2017; Proskurnikov_2017]. To test the
influence of data quantity on multilayer networks, we generate multilayer networks
using a subset of observations. Variance decreased across all
network metrics in all three habitat layers with increasing number of
observations. Individual graph strength showed high variability at low number of
observations, while edge overlap and multidegree increased sharply. After
approximately 200 observations, the rate of change for all metrics decreased and
and graph strength remained relatively static, while edge overlap and
multidegree continued to increase slowly. As more observations were added, rarer
relationships were recorded revealing the value of this form of sensitivity
analysis. Finally, due to the autocorrelated nature of biologging data it is
essential to ensure social association data area non-randomly distributed
[@Farine_2017b].
<!-- nobs -->
